---
title: "Lauren_Assignment_9_markdown"
output: html_document
date: "2023-03-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Assigment # 9
Creating 4 different prediction models based on Graduate School Admissions Data. 

The followig shows statistical information about the performance of each model



```{r}
library(modelr)
library(easystats)
library(broom)
library(tidyverse)
library(fitdistrplus)
library(janitor)
library(patchwork)

dat <- read_csv("../../Data/GradSchool_Admissions.csv")
dat$admit <- as.logical(dat$admit)  
dat$rank <- as.factor(dat$rank)

mod1 <- glm(data = dat,
            formula = admit ~ (gre + gpa) * rank,
            family = "binomial")
summary(mod1)

mod2 <- glm(data = dat,
            formula = admit ~ (gre * gpa) + rank,
            family = "binomial")
summary(mod2)

mod3 <- glm(data = dat,
            formula = admit ~ gre * gpa * rank,
            family = "binomial")
summary(mod3)

mod4 <- glm(data = dat,
            formula = admit ~ gre * gpa,
            family = "binomial")
summary(mod4)
```

Creating a plot that compares my 4 models
```{r}
compare_performance(mod1,mod2,mod3,mod4) %>% plot()
```

Plotting some predictions

```{r}
library(modelr)
library(easystats)
library(broom)
library(tidyverse)
library(fitdistrplus)
library(janitor)
library(patchwork)
add_predictions(dat, mod2, type = "response") %>% 
  ggplot(aes(x= gpa, y = pred, color = rank, group= rank)) +
  geom_smooth(se = FALSE) +
  theme_minimal()

add_predictions(dat, mod2, type = "response") %>% 
  ggplot(aes(x=gre, y=pred, color= rank, group=rank)) +
  geom_smooth(se = FALSE) +
  theme_minimal()
```

If this HTML looks horrible, please note I was not present in this lecture.
No recording of the class was provided.

I was constipated -haven't pooped in 4 days. Any advise?
